Denotational Semantics of Gradual Typing using Synthetic Guarded Domain Theory

### 2024-10-25 paper-new/concrete-relational-model.tex
small wording change in concrete relational model section

The term semantics $\sem{M}$ is nearly identical to the term semantics in
Section~\ref{sec:concrete-term-model}. One difference is that the interpretation
of the function type $A_i \ra A_o$ in the term semantics of Section
\ref{sec:concrete-term-model} involves \emph{arbitrary functions}, while the
interpretation of the function type in the term semantics defined here involves
only those functions that are morphisms of predomains. Additionally, the
semantics of casts is slightly different. In the semantics of Section
\ref{sec:concrete-term-model}, the projection corresponding to the type
precision $cc'$ is simply the composition of the projections. In the new
semantics, the corresponding projection involves a perturbation. The reason for
this is technical and is a consequence of the construction of the composition of
value/computation relations. (The relevant projection is defined in the proof of
Lemma \ref{lem:representation-comp-F-U} in the Appendix.) However, the two
projections are extensionally equivalent since they are the same up to a
perturbation.

>>>>

The term semantics $\sem{M}$ is nearly identical to the term semantics in
Section~\ref{sec:concrete-term-model}. One difference is that the interpretation
of the function type $A_i \ra A_o$ in the term semantics of Section
\ref{sec:concrete-term-model} involves \emph{arbitrary functions}, while the
interpretation of the function type in the term semantics defined here involves
only those functions that are morphisms of predomains. Additionally, the
semantics of casts is slightly different. In the semantics of Section
\ref{sec:concrete-term-model}, the projection corresponding to the type
precision $cc'$ is simply the composition of the projections. In the new
semantics, the corresponding projection involves a perturbation. This is a
consequence of the construction of the composition of value/computation
relations (the relevant projection is defined in the proof of Lemma
\ref{lem:representation-comp-F-U} in the Appendix). However, the two projections
are extensionally equivalent since they are the same up to a perturbation.
